---
title: "Hope this will work"
author: "jiaying"
date: "9/15/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning assessment: Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

**The chunk below creates a datafram comprised of a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element.Then, it produces a histogram of the absolute value variable just created with an inline summary giving the median value rouded to two decimal places.**

```{r Learning Assessment1, echo = FALSE}
library(tidyverse)

assessment_df = tibble(
  num_vec = rnorm(500, mean = 1),
  log_vec = num_vec > 0,
  abs_vec = abs(num_vec)
)


ggplot(assessment_df, aes(x = abs_vec)) + geom_histogram()

medium_assessment = median(pull(assessment_df,num_vec))
```
The median of the variable containing absolute values is 
`r round(medium_assessment, digits = 2)`.



